Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-14 paper.qmd
Added trimesh of PaCMAP

trimesh_removed_mnist <- vis_rmlg_mesh(
  distance_edges = distance_mnist, 
  benchmark_value = benchmark_mnist, 
  tr_coord_df = tr_from_to_df_mnist, 
  distance_col = "distance") +
  #xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("a", sc_ltr_pos_mnist)

@@

<!--add langevitour screenshots and youtube animation link-->

>>>>

trimesh_removed_mnist <- vis_rmlg_mesh(
  distance_edges = distance_mnist, 
  benchmark_value = benchmark_mnist, 
  tr_coord_df = tr_from_to_df_mnist, 
  distance_col = "distance") +
  geom_point(data = pacmap_minst_scaled,
             aes(
               x = PaCMAP1,
               y = PaCMAP2
             ),
             alpha=0.5, 
             size = 0.1) +
  interior_annotation("a", sc_ltr_pos_mnist)

@@

<!--add langevitour screenshots and youtube animation link-->
```{r}
trimesh_removed_mnist 
```
